%!TeX root = distribution
\documentclass[paper.tex]{subfiles}
\begin{document}
	
\begin{center}
	{\bf \cite{Microwave2009} already mention this inhomogeneity; \cite{Elastic} perform a much better analysis than we do.}
\end{center}
	

\cite{Efficient2015} theoretically model the virus to determine the minimum electric field required to destroy it. 

They assume that the virus is a simple damped harmonic oscillator, where the 'core' and 'shell' oscillate in opposition. 

They determine the net charge experimentally from microwave absorption measurements.



Since \cite{Efficient2015} try to compute the {\it threshold} field to obtain some amount of inactivation, they use a value of 400 piconewtons for the breaking stress of the envelope, obtained from \cite{Bending2011}. This threshold value agrees very well with their experimental data. However, \cite{Bending2011} also mentions that 

\begin{quote}
	More than 95\% [of] puncture events occurred above 0.4 nN.
\end{quote}

Inputting this yield stress distribution produces an inactivation field distribution that is far higher than that of \cite{Efficient2015}'s experimental data by some 200 V/m.

Let us therefore re-examine the microwave spectrum. Much of this data was found in order to try to simulate the inactivation mechanism by molecular dynamics, so it was not a complete waste of time.

The liposome breaking force is distributed in an obstinately non-gaussian bimodal manner, so we override the covariance matrix and introduce a gaussian KDE sampled from the force histogram in \cite{Bending2011}.

Lorentzian


"95%.".

The distribution of breaking strengths in [Li 2011] (Figure 5b) is bimodal, and a naive gaussian fit does not produce the above 95\% figure.

Smudged 

The simple-harmonic

This problem has a long history, stretching back to Cole-Cole's landmark 1942\cite{Dispersion1941} paper and \cite{Electrical1941}. Such concerning statements as 'mathematically ill-posed' are bandied about; however, standard optimization techniques work fine.

\begin{quote}
	As Fuoss and Kirkwood have shown, it is possible to calculate the distribution necessary to account for any given experimental results from the observed $\epsilon''$ - frequency relation.
\end{quote}

Within a sample of a single species, there is $\approx$ 12.7\%  ($109 \pm 16.65 \text{ nm}$\cite{lauffer1944biophysical}, $115 \pm 12 \text{ nm}$ \cite{Characterization1984}) variation in diameter and  \cite{Characterization1984} variation in mass.



Note that, per \cite{lauffer1944biophysical}, of Inf. A and B, "the infectious particles have diameters within the range 80 to 135[nm]". \cite{Efficient2015}'s MDCK plaque assay is already sensitive to infectivity; the extreme-sized non-infective mutants would already be filtered out. Their PCR assay might not be; the DNA of all non-infectious mutants would be considered.


Worse still, influenza exhibits pleiomorphy, stretching into a variety of \cite{Influenza2006}; 

Charge can be determined by the primary structure sequence. A table of net charges of Inf. A, and T4. however, a few influzena proteins have been found to have anomalous secondary structure charge.



Because CryoEM uses charged particles, it is technically feasible to determine the net charge distribution in the whole virus using an ingenious \cite{Identification2018} technique. However, this has not yet been implemented in any


\footnotemark

\footnotetext{
	It has been shown that, over decades, single species of viruses can effect large-scale changes in the net charges of their proteins without altering their function\cite{Dynamics2010}. Use of this technique will provide a selection bias towards immunity to electromagnetic fields. We do not have the biological knowledge to determine whether this is plausible; it simply seemed worth mentioning. 
	
}

NCoV is closer to \cite{Viral2020}, but does not appear to exhibit pleiomorphy.

A cursory fit found parameters $\bar{\text{Q}}$=3.736,  $\sigma \ \text{Q} = $0.738, $\bar{F}_{res}=$8.606 GHz and $\sigma {F_{res}}=$1.073 \st{and covariance of +1.001}\footnote{warning}. This describes the observed spectrum equally well as Q=2.0:

We have not yet determined whether these values also explain the other datasets in \cite{Efficient2015}, such as the inactivation vs frequency plot.


T4 bacteriophage has far greater restraint, with only a 2.5\% $\pm \sigma$ variation in the dimensions of the icosahedral head \cite{Head1988}.\footnotemark

\footnotetext{T4 also occasionally finds itself as an isometric mutant (See PDB 5VF3).} 


Plugging a (single, non-distributed, which must be fixed; FIXME) Q of 3.75 into the above breaking force distribution, and applying some guesses for the covariance of various parameters, we get:

								Yang get:
6th percentile: 59.234       68 V/m
38th percentile: 127.376		87 V/m
63th percentile: 186.803		171 V/m
90th percentile: 298.882     100\% 275 V/m
99.9th percentile: 565.126 

Of course, 
\begin{quote}
	With four parameters I can fit an elephant, and with five I can make him wiggle his trunk. \\- J.v.N.
\end{quote}

and here we have some dozen parameters. So these approximations should be regarded with skepticism.

Since this entire covariance process will have to be repeated for SARS-NCoV \footnotemark we have not bothered to fine-tune any of these fits; and so the idea that the Q-factor is higher than previously reported must still be regarded as only a speculative hypothesis.

\footnotetext{...the CoV of NCoV}

This introduces a self-evident optimization: rather than applying a pulse of a single frequency, the pulses should be swept across the distribution. From the (extremely crude) approximations on Inf. A above, this has little effect on $<$ 90-th percentile virions, but decreases the inactivation field of the last 10\% by perhaps 50 V/m.

In practice, not having a single frequency to design a microwave system around makes the engineering quite a bit more difficult whether this tradeoff is worth making depends. "Broadbanding" makes all the $\lambda / 4$ structures behave rather poorly; depending on the bandwidth required, biasing may need to be made inductive or resistive.

In the case of patch antennas for phased arrays, U-slots have to be added to dull the impedance bandwidth; all sorts of free-space injection-locking techniques become untenable; waveguides and cavities start to run into overlapping transmission modes. Structures like magnetron cavities are hard to 

For the pre-engineered, off-the-shelf clinical without cost constraints, this is probably not a serious issue.

It may be useful to choose a few 

Are such high pulse powers achievable? 




	

\end{document}