
\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Acknowledgements}\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This paper is not novel enough to deserve this chapter, but those to be acknowledged are.

The authors of the original papers deserve the credit for this entire work;  it is rare that such a monumental finding is served on a silver platter.

Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work. 

Dr. Dainis' videos on microbiological technique were also useful.

Thanks to the professors at York and beyond for returning my emails. 

Thanks to L.H. for wisdom regarding this project.

Thanks to P.B and H.P. for tolerating ramblings and M. for the hug.

Special thanks to all the people - most equally capable of writing this paper if provided the opportunity - who work menial shifts at the component suppliers that remained open that were so critical. Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck. 

Chiefly among the enablers are of course my parents, Doris and Brian, without whom this work would have been done by someone else, and who also supported this work financially. 


The authors acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for developing and making the AustinMan and AustinWoman human body models available at https://sites.utexas.edu/austinmanaustinwomanmodels/.

One Very Important Thought



{\Large <3}

